---
title: <span style="font-size:125%; font-family:Sans Source">SIMS Summary params:OU_Name FY22 </span>
author: "Ryan Carroll"
date: "11/7/2022"
output: 
  pdf_document
params: 
  OU_Name: OU_Name
  data: "sims_mock.csv"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}

library(readr)
library(tidyverse)
library(ggplot2)
library(knitr)
library(rmarkdown)
library(glitr)

#devtools::install_github("USAID-OHA-SI/glitr")
#tinytex::install_tinytex()

sims_all <- read_csv("C:/Users/rcarroll/Desktop/Git/Evaluation/Sims Pull/SIMS_Pull.csv")



sims_mock <- sims_all %>%
  rename(OU_Name = `OU Name`) %>%
  filter(OU_Name == "Burundi" | OU_Name == "Namibia") %>%
  filter(`Assessment FY` == "2022")

```
```{r include=FALSE}
# All Necesary calcs for report below

count_assessments <- sims_mock %>%
  filter(OU_Name == params$OU_Name) %>%
  distinct(`Assessment ID`) %>%
  nrow()


count_followups <- sims_mock %>%
  filter(OU_Name == params$OU_Name) %>%
  filter(`Follow Up Status` == "Completed") %>%
    distinct(`Assessment ID`) %>%
  nrow()

count_missed_followups <- sims_mock %>%
  filter(OU_Name == params$OU_Name) %>%
filter(`Follow Up Status` == "Missed") %>%
    distinct(`Assessment ID`) %>%
  nrow()
```

# SIMS Summary for `r params$OU_Name`

## This report summarizes key findings from the last FY of completed SIMS assessments. In FY22, `r count_assessments` assessments were completed in `r params$OU_Name`.

#	In total, `r count_followups` follow-up assessments have been reported (while `r count_missed_followups` assessments have been missed). 

#- Flag for discussion with the OU cluster team: What are your plans for follow-up assessments and for assessing program quality in the coming COP cycle, given that many follow-up assessments have been missed?



```{r}

 # r <- sims_mock %>%
 #  filter(OU_Name == params$OU_Name) %>%
 #  distinct(OU_Name)

#knitr::kable(r)


 
# for (i in unique(sims_mock$OU_Name)) {
#   
#   
#   knitr::kable(r)
# 
# }




#kable(r)



```

```{r}




# b <- sims_mock %>%
   #filter(OU_Name == params$OU_Name) %>%
    b <- print(ggplot(sims_mock, aes(x = `Score for Green`, y = `Score for Red`))+
    geom_jitter())
#   
  # scale_color_si("denim") +
  # si_style()


# for (i in unique(sims_mock$OU_Name)) {
# 
# 
# c <-  print(ggplot(sims_mock, aes(x = `Score for Green`, y = `Score for Red`))+
#    geom_count())
# 
#   
# 
# 
# }

plot(b)
```
